---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here:

## Exercise 1

Explain what you are visualizing here:

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE
  

```

## Exercise 2

Explain what you are visualizing here:

Put your figure here:

```{r exercise2,echo=FALSE}

####PUT YOUR CODE HERE
  
```

## Exercise 3

Explain what you are visualizing here:

Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE

```

## Exercise 4

Explain what you are visualizing here:

Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE

```
