---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: LAU LOUIS KIN PONG



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
cces <- cces %>% mutate(ideo5 = recode(ideo5,
                                      "5" = "Very Conservative",
                                      "4" = "Conservative",
                                      "3" = "Moderate",
                                      "2" = "Liberal",
                                      "1" = "Very Liberal"))

cces %>% ggplot(aes(x=ideo5, fill=ideo5))+
  geom_bar()+
  guides(fill=FALSE)+
  labs(title="Respondent Ideology", x="Ideology", y="Count")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
cces <- cces %>% mutate(pew_religimp = recode(pew_religimp,
                                      "4" = "Not imp.",
                                      "3" = "Not too imp.",
                                      "2" = "Somewhat imp.",
                                      "1" = "Very imp."))

cces %>% ggplot(aes(x=pew_religimp, fill=factor(ideo5)))+
  geom_bar()+
  labs(title="Importance of Religion by Ideology", x="Importance of Religion", y="Count", fill="Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
dat <-expand_grid(Semester=1:6, Student=c("Amanda","Betty","Carol"))
dat$Grade <- round(runif(18,80,100))

ggplot(dat, aes(x=Semester, y=Grade,color=Student))+
  geom_line()+
  labs(title = "Student Grades by Semester")+
  guides(color=FALSE)+
  facet_grid(~Student)
```
